%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Algorithm Engineer} % Job title
    {\href{https://damo.alibaba.com}{DAMO Academy}, Alibaba Group} % Organization
    {Hangzhou, China} % Location
    {July. 2018 -} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research on some computer vision projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {iDST, Alibaba Group} % Organization
    {Beijing, China} % Location
    {June. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {GAN-based style-transferring.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Master Student} % Job title
    {\href{https://www.waseda.jp/fsci/gips/en/}{Graduate School of Information, Production and Systems (IPS)}, Waseda University} % Organization
    {Kitakyushu, Japan} % Location
    {Sept. 2016 - March 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team member of \href{http://www.waseda.jp/sem-hflab/nclab/index.html}{Neurocomputing System Lab}, supervised by \href{http://www.f.waseda.jp/jinglu/}{Prof. Takayuki Furuzuki}.}
        \item {Cascade Fully Convolutional Networks for object boundary detection.}
        \item {Won the Japanese Government (Monbukagakusho:MEXT) Scholarship in 2016.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Master Student} % Job title
    {School of Communication and Information, \href{http://www.shu.edu.cn}{Shanghai University}} % Organization
    {Shanghai, China} % Location
    {Sept. 2015 - July. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team member of Computer Vision and Pattern Recognition Lab, supervised by \href{http://wei-shen.weebly.com}{Prof. Wei Shen}.}
        \item {Object proposal, symmetry detection, edge detection and shape recognition.}
        \item {1 CVPR, 1 TIP, 1 ICCV and 2 PRLs.}
        \item {Won the Guanghua Scholarship in 2017.}
      \end{cvitems}
    }

%---------------------------------------------------------
%---------------------------------------------------------
\end{cventries}
